Supplementary Information

### 2020-08-26 doc/manuscript/MEE_manuscript.Rmd
update results
#66

**The relative importance of $DBH$ and climate shifted across growth metrics and climates (Figs. 5, S#_#).** (*It will be easier to fill this in once we complete [ISSUE #66 in ForestGEO-climate-sensitivity ](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/66)*).
The relative importance of $DBH$ tended to be least for $\Delta r$, intermediate for $BAI$, and highest for $\Delta AGB$ (e.g., at SCBI; Fig. **5**).
However, there were exceptions (e.g., at Little Tesuque; Fig. **5**).
The relative importance of climate was modest at sites including SCBI, ..., and stronger at sites including Little Tesuque, ... (Figs **5**, **S#**-**S#**).

>>>>

**The relative importance of $DBH$ and climate shifted across growth metrics and climates (Figs. **5**, **S5**-**S14**).** 
The relative importance of $DBH$ tended to be least for $\Delta r$, intermediate for $BAI$, and highest for $\Delta AGB$ (e.g., at SCBI; Fig. **5**).
However, there were exceptions, particularly when $\Delta r$ decreased steeply with $DBH$ (e.g., at Little Tesuque; Fig. **5**).
The relative importance of climate was modest at sites including SCBI (Fig. **5**), HF (Fig. **S11**), and SC (Fig. **S14**), and stronger at sites including LT (Fig. **5**) and BCI (Fig. **S5**).
